The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-06 manuscript/manuscript.Rnw
fix up dog paragraph

The top 50 non-housekeeping expressed genes as measured by \ac{FPKM}
in the term placenta of \dog are shown in
\cref{tab:top50_dog_placenta} with a list of all genes in Supplemental
\cref{tab:all_canis_familiaris_placenta}. The gene with the highest
expression %
(\Sexpr{gene.expression("canis familiaris","TMSB10")}) is the thymosin 
\textit{TMSB10} %
(\Sexpr{gene.expression("canis familiaris","ENSCAFG00000002115")}) %
is the hormone relaxin (\textit{RLN2}). Other highly expressed genes
among the top 50 (\cref{tab:top50_dog_placenta}) include genes
involved in the cytoskeleton (\textit{TMSB10}, \textit{TMSB4X}),
anticoagulation (\textit{TFPI2}, \textit{PLA2G7}), innate immunity
(\textit{LCN2}, \textit{GM2A}), lipid metabolism (\textit{APOE}),
inhibition of matrix metalloproteinases (\textit{TIMP2},
\textit{TIMP3}), and growth factors (\textit{PGF}, \textit{EGFR},
\textit{HTRA1}). The gene \textit{LGALS1}, which shows evidence of
immunosupression during pregnancy
\cite{Than.ea2008:Emergenceofhormonaland}, is highly expressed %
(\ac{FPKM}=\Sexpr{gene.expression("canis familiaris","LGALS1")}). %
In addition, an ortholog of SSLP1 (ENSCAFG00000010638) a gene
expressed in the placentas of \cow (%
\Sexpr{gene.expression("bos tarus","SSLP1")}, %
\cref{tab:top50_cow_placenta}) and \sheep
(\Sexpr{gene.expression("ovis aries","SSLP1")},
\cref{tab:top50_sheep_placenta}) but is not present in primates
\cite{Ushizawa.ea2009:Characterizationandexpressionanalysis}
(\cref{fig:sslp1_evolution_tree}), is also expressed at high levels
%
(\ac{FPKM}=\Sexpr{gene.expression("canis familiaris","ENSCAFG00000010638")}). %
There is no placental expression of the estrogen synthase gene
(\textit{CYP19A1}) in \dog (\cref{fig:estrogen_evolution_tree}), 
however expression of \textit{HSD3B1} is relatively high
(\ac{FPKM}=\Sexpr{gene.expression("canis familiaris","HSD3B1")}).

>>>>

The top 50 non-housekeeping expressed genes as measured by \ac{FPKM}
in the term placenta of \dog are shown in
\cref{tab:top50_dog_placenta} with a list of all genes in Supplemental
\cref{tab:all_canis_familiaris_placenta}. The gene with the highest
expression %
(\Sexpr{gene.expression("canis familiaris","TMSB10")}) is the thymosin 
\textit{TMSB10} %
(\Sexpr{gene.expression("canis familiaris","ENSCAFG00000002115")}) %
is the hormone relaxin (\textit{RLN2}). Other highly expressed genes
among the top 50 (\cref{tab:top50_dog_placenta}) include genes
involved in the cytoskeleton (\textit{TMSB10}, \textit{TMSB4X}),
anticoagulation (\textit{TFPI2}, \textit{PLA2G7}), innate immunity
(\textit{LCN2}, \textit{GM2A}), lipid metabolism (\textit{APOE}),
inhibition of matrix metalloproteinases (\textit{TIMP2},
\textit{TIMP3}), and growth factors (\textit{PGF}, \textit{EGFR},
\textit{HTRA1}). The gene \textit{LGALS1}, which shows evidence of
immunosupression during pregnancy
\cite{Than.ea2008:Emergenceofhormonaland}, is highly expressed %
(\Sexpr{gene.expression("canis familiaris","LGALS1")}). %
In addition, an ortholog of \textit{SSLP1} (ENSCAFG00000010638) a gene
expressed in the placentas of \cow (%
\Sexpr{gene.expression("bos taurus","SSLP1",complete=TRUE)}, %
\cref{tab:top50_cow_placenta}) and \sheep
(\Sexpr{gene.expression("ovis aries","SOLD1",complete=TRUE)},
\cref{tab:top50_sheep_placenta}) but is not present in primates
\cite{Ushizawa.ea2009:Characterizationandexpressionanalysis}
(\cref{fig:sslp1_evolution_tree}), is also expressed at high levels
%
(\Sexpr{gene.expression("canis familiaris","ENSCAFG00000010638")}). %
There is no placental expression of the estrogen synthase gene
(\textit{CYP19A1}) in \dog 
(\Sexpr{gene.expression("canis familiaris","CYP19A1")}
\cref{fig:estrogen_evolution_tree}), 
and expression of \textit{HSD3B7} is also low
(\Sexpr{gene.expression("canis familiaris","HSD3B7")}, 
\cref{fig:progesterone_evolution_tree}).
